%_____________________________________________________________________________________________
% LATEX Template: Department of Comp/IT BTech Project Reports
% Abstract of Report
% Sun Mar 27 10:34:00 IST 2011
%_____________________________________________________________________________________________
\newpage
%\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
\begin{center}
\Large \textbf{Abstract}
\end{center}
Every product development starts with idea conceptualization and design. The ideators’ and designers’ first choice is sketching the idea to conceptualize the product. After a few iterations of product design mockups/prototypes are passed on to developers who have the job to convert these designs into a functional product by grasping the design concepts and using their coding skills. Work stops whenever one discipline finishes a portion of the project and passes responsibility to another discipline. Our service leverages computer vision and machine learning, to automate the typical task of converting mockups to websites and help the developer focus on the minute details of the design. As a proof of concept this project we will be focussing on web mockups but the functionality can be easily extended to mobile applications too.
This service will consist of two stages firstly accepting images of web mockups, hand-drawn sketches and identifying the various HTML components in the sketch using Convolutional Neural Networks and tag them appropriately, secondly, the identified components will be converted to code based on HTML5, Flexbox, React and Bootstrap.
The service will try and bridge the gap between designers and developers by simplifying the product development process and hence offer end to end solution. This will also help people with little or almost no knowledge of web development to bring their design ideas into reality.
 
%\end{abstract}

%_____________________________________________________________________________________________
