%_____________________________________________________________________________________________
% Department of Comp/IT BTech Project Report
%_____________________________________________________________________________________________
\begin{thebibliography}{20}

  \bibitem{notes} Tony Beltramelli: pix2code: Generating Code from a Graphical User Interface Screenshot "\url {https://arxiv.org/pdf/1705.07962.pdf}"
  \bibitem{notes} M. Balog, A. L. Gaunt, M. Brockschmidt, S. Nowozin, and D. Tarlow. Deepcoder: Learning to write programs.arXiv preprint arXiv:1611.01989, 2016.
  \bibitem{notes} I. Goodfellow, J. Pouget-Abadie, M. Mirza, B. Xu, D. Warde-Farley, S. Ozair, A. Courville, andY. Bengio. Generative adversarial nets. In Advances in neural information processing systems,pages 2672–2680, 2014.
  \bibitem{notes} S. Reed, Z. Akata, X. Yan, L. Logeswaran, B. Schiele, and H. Lee. Generative adversarial text to image synthesis. In Proceedings of The 33rd International Conference on Machine Learning,volume 3, 2016
  \bibitem{notes} S. Koike Adaptive threshold nonlinear algorithm for adaptive filters with robustness against impulse noise. In IEEE Transactions on Signal Processing (Volume: 45, Issue: 9, Sep 1997)
  \bibitem{notes} Ruchi Manish Gurav, Premanand K. Kadbe  Real time finger tracking and contour detection for gesture recognition using OpenCV. In  2015 International Conference on Industrial Instrumentation and Control (ICIC)
  \bibitem{notes} Imran Sarwar Bajwa, Imran Siddique, M. Abbas Choudhary Web Layout Mining (WLM): A New Paradigm for Intelligent Web Layout Design. In 2006 ITI 4th International Conference on Information and Communications Technology.
  \bibitem{notes} Rich feature hierarchies for accurate object detection and semantic segmentation https://arxiv.org/abs/1311.2524
  \bibitem{notes} Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks. https://arxiv.org/abs/1506.01497
  \bibitem{notes} You Only Look Once: Unified, Real-Time Object Detection. https://arxiv.org/abs/1506.02640
  \bibitem{notes} An Overview of the Tesseract OCR Engine. https://research.google.com/pubs/archive/33418.pdf

\end{thebibliography}
%_____________________________________________________________________________________________
